QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-2.2.tex
bugfix and minor changes in QP classes

 \item \emph{Convex Integer Quadratic Programs} \textit{CGC} are, in general, $\mathcal{NP}$-hard, and therefore require enumerative techniques to be solved. However, convexity of the objective function and constraints implies that efficient techniques (see \textit{CCC}) can be used at least to solve continuous relaxations. The general view is that \textit{CGC} are not, all other things being equal,  substantially more difficult than \textit{LGL} to solve, especially if the objective function and/or the constraints have specific properties (e.g., \textit{DGL}, \textit{CGL}). Often integer variables are in fact binary ones, so several \textit{CCC} models are \textit{C}\{\textit{B},\textit{M}\}\textit{C} ones. In practice binary variables are considered to lead to somewhat easier problems than general integer ones (cf.~the cited result about hardness of unbounded integer quadratic programs), and several algorithmic techniques have been specifically developed for this special case. However, the general approaches for \textit{CBC} are basically the same as for \textit{CGC}, so there is seldom the need to distinguish between the two classes as far as solvability is concerned, although matters can be different regarding actual solution cost. Programs with only binary variables \textit{CBC} can be easier than mixed-binary or integer ones \textit{C}\{\textit{M},\textit{I}\}\textit{C} because some techniques are specifically known for the binary-only case, cf.~the next point \cite{BEP09}. Absence of continuous variables, even in the presence of integer ones \textit{CIC}, can also lead to specific techniques \cite{BEL13}.

@@

  \item \emph{Nonconvex Binary Quadratic Programs} \textit{QB}\{\textit{B}, \textit{N}, \textit{L}\} obviously are $\mathcal{NP}$-hard. However, the special nature of binary variables combined with quadratic forms allows for quite specific techniques to be developed, one of which is the reformulation of the problem as a \textit{LBL}. Also, many well-known combinatorial problems can be naturally reformulated as problems of this class, and therefore a considerable number of results have been obtained by exploiting specific properties of the set of constraints \cite{Rendl2008,Loiola2007657}.

@@

  \item \emph{Nonconvex Integer Quadratic Programs} \textit{QGQ} is the most general, and therefore is the most difficult, class. Due to the lack of convexity even when integrality requirements are removed, solution methods must typically combine several algorithmic ideas, such as enumeration (distinguishing the role of integral variables from that of continuous ones involved into nonconvex terms) and techniques (e.g., outer approximation, semidefinite programming relaxation, \ldots) that allow the efficient computation of bounds. As in the convex case, \textit{QBQ}, \textit{QMQ}, and \textit{QIQ} can benefit from more specific properties of the variables \cite{Buchheim2013,Dong2016}.

>>>>

 \item \emph{Convex Integer Quadratic Programs} \textit{CGC} are, in general, $\mathcal{NP}$-hard, and therefore require enumerative techniques to be solved. However, convexity of the objective function and constraints implies that efficient techniques (see \textit{CCC}) can be used at least to solve continuous relaxations. The general view is that \textit{CGC} are not, all other things being equal,  substantially more difficult than \textit{LGL} to solve, especially if the objective function and/or the constraints have specific properties (e.g., \textit{DGL}, \textit{CGL}). Often, integer variables are in fact binary ones, so several \textit{CGC} models are \textit{C}\{\textit{B},\textit{M}\}\textit{C} ones. In practice, binary variables are considered to lead to somewhat easier problems than general integer ones (cf.~the cited result about hardness of unbounded integer quadratic programs) and several algorithmic techniques have been specifically developed for this special case. However, the general approaches for \textit{CBC} are basically the same as for \textit{CGC}, so there is seldom the need to distinguish between the two classes as far as solvability is concerned, although matters can be different regarding actual solution cost. Programs with only binary variables (\textit{CBC}) can be easier than mixed-binary or integer ones (\textit{C}\{\textit{M},\textit{I}\}\textit{C}) because some techniques are specifically known for the binary-only case, cf.~the next point \cite{BEP09}. Absence of continuous variables, even in the presence of integer ones (\textit{CIC}), can also lead to specific techniques \cite{BEL13}.

@@

  \item \emph{Nonconvex Binary Quadratic Programs} \textit{QB}\{\textit{B},\textit{N},\textit{L}\} obviously are $\mathcal{NP}$-hard. However, the special nature of binary variables combined with quadratic forms allows for quite specific techniques to be developed, one of which is the reformulation of the problem as a \textit{LBL}. Also, many well-known combinatorial problems can be naturally reformulated as problems of this class, and therefore a considerable number of results have been obtained by exploiting specific properties of the set of constraints \cite{Rendl2008,Loiola2007657}.

@@

  \item \emph{Nonconvex Integer Quadratic Programs} \textit{QGQ} is the most general, and therefore is the most difficult, class. Due to the lack of convexity even when integrality requirements are removed, solution methods must typically combine several algorithmic ideas, such as enumeration (distinguishing the role of integral variables from that of continuous ones involved in nonconvex terms) and techniques that allow the efficient computation of bounds (e.g., outer approximation, semidefinite programming relaxation, \ldots). As in the convex case, \textit{QBQ}, \textit{QMQ}, and \textit{QIQ} can benefit from more specific properties of the variables \cite{Buchheim2013,Dong2016}.
